Expectations, Outcomes, and Challenges \\ of Modern Code Review

### 2013-03-16 paper.tex
moved sections into a separate dir
done up to section IV (partially included)
working on section 4
done with section 5
did another full pass on the paper
changed according to camera-ready formatting instructions

\usepackage{graphicx}\graphicspath{{figs/}}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{xspace}
\usepackage{listings}
\usepackage{ifthen}
\usepackage{float} % defines newfloat used below
\usepackage[sort&compress]{natbib} 
%\usepackage{todos} % Use \todoset{all=off} to turn off todos in a paper.
\usepackage{booktabs}
\usepackage{fancyhdr}
\usepackage{microtype}

% hyperref redefines a number of macros, so it should be last.  Empirically,
% doing so eliminates compiler warnings.
\usepackage[bookmarks, colorlinks, citecolor=green, urlcolor=blue,
			filecolor=blue, linkcolor=blue]{hyperref}
% According to the hyperref readme, algorithm must follow hyperref

@@

% English
\newcommand{\cf}{\hbox{\emph{cf.}}\xspace}
\newcommand{\deletia}{\ldots [deletia] \ldots}
\newcommand{\etal}{\hbox{\emph{et al.}}\xspace}
\newcommand{\eg}{\hbox{\emph{e.g.}}\xspace}
\newcommand{\ie}{\hbox{\emph{i.e.}}\xspace}
\newcommand{\scil}{\hbox{\emph{sc.}}\xspace} %scilicet: it is permitted to know
\newcommand{\st}{\hbox{\emph{s.t.}}\xspace}
\newcommand{\wrt}{\hbox{\emph{w.r.t.}}\xspace}
\newcommand{\etc}{\hbox{\emph{etc.}}\xspace}
\newcommand{\viz}{\hbox{\emph{viz.}}\xspace} %videlicet: it is permitted to see
\newcommand{\vs}{\hbox{\emph{vs.}}\xspace}

@@

\usepackage{mdframed}
%% Document-specific hyperref options
\hypersetup{
pdftitle={Expectations, Outcomes, and Challenges of Modern Code Review},
    pdfauthor={Alberto Bacchelli and Christian Bird},
    plainpages=false,
    linkcolor=black, % Overriding these colors to black is somewhat unfortunate 
    %citecolor=black, % b/c the defaults are useful in color.
    citecolor=blue, % b/c the defaults are useful in color.
    filecolor=black,
    urlcolor=black,
    pdfpagelabels
}

@@

@@

\author{
	\begin{tabular}{ccc}
		Alberto Bacchelli & \hspace{0.5in} & Christian Bird \\
		REVEAL @ Faculty of Informatics & & Microsoft Research \\
		University of Lugano, Switzerland & & Redmond, Washington, USA \\
		\texttt{alberto.bacchelli@usi.ch} &  &\texttt{cbird@microsoft.com}
	\end{tabular}
}

@@

\input{introduction}
\input{related_work}
\input{methodology}
\input{expectations}
\input{outcomes}
\input{challenges}
\input{implications}
\input{limitations}
\input{conclusion}

\bibliographystyle{abbrv}
%\setlength{\bibsep}{3pt}
\small
\bibliography{paper}

>>>>

\usepackage{graphicx}\graphicspath{{figs/}}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{xspace}
\usepackage{listings}
\usepackage{ifthen}
\usepackage{float} % defines newfloat used below
%\usepackage[sort&compress]{natbib} % <<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<< commented out
%\usepackage{todos} % Use \todoset{all=off} to turn off todos in a paper.
\usepackage{booktabs}
\usepackage{fancyhdr}
\usepackage{microtype}
\usepackage{paralist}

% hyperref redefines a number of macros, so it should be last.  Empirically,
% doing so eliminates compiler warnings.
\usepackage{hyperref}
% According to the hyperref readme, algorithm must follow hyperref

@@

% English
\newcommand{\cf}{\hbox{\emph{cf.}}\xspace}
\newcommand{\deletia}{\ldots [deletia] \ldots}
\newcommand{\etal}{\hbox{\emph{et al.}}\xspace}
\newcommand{\eg}{\hbox{\emph{e.g.},}\xspace}
\newcommand{\ie}{\hbox{\emph{i.e.},}\xspace}
\newcommand{\scil}{\hbox{\emph{sc.}}\xspace} %scilicet: it is permitted to know
\newcommand{\st}{\hbox{\emph{s.t.}}\xspace}
\newcommand{\wrt}{\hbox{\emph{w.r.t.}}\xspace}
\newcommand{\etc}{\hbox{\emph{etc.}}\xspace}
\newcommand{\viz}{\hbox{\emph{viz.}}\xspace} %videlicet: it is permitted to see
\newcommand{\vs}{\hbox{\emph{vs.}}\xspace}

\newcommand{\cat}[1]{{\textsc{#1}}}

@@

%\usepackage{mdframed} <<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<< commented out
%% Document-specific hyperref options
\hypersetup{
pdftitle={Expectations, Outcomes, and Challenges of Modern Code Review},
    pdfauthor={Alberto Bacchelli and Christian Bird},
    plainpages=false,
    linkcolor=black, % Overriding these colors to black is somewhat unfortunate 
    %citecolor=black, % b/c the defaults are useful in color.
    citecolor=blue, % b/c the defaults are useful in color.
    filecolor=black,
    urlcolor=black,
    pdfpagelabels
}

@@

\newcommand{\figref}[1]{Figure~\ref{#1}\xspace}

@@

\author{
	\begin{tabular}{ccc}
		Alberto Bacchelli & \hspace{0.5in} & Christian Bird \\
		REVEAL @ Faculty of Informatics & & Microsoft Research \\
		University of Lugano, Switzerland & & Redmond, Washington, USA \\
		alberto.bacchelli@usi.ch &  & cbird@microsoft.com
	\end{tabular}
}

@@

\input{sections/introduction}
\input{sections/related_work}
\input{sections/methodology}
\input{sections/expectations}
\input{sections/outcomes}
\input{sections/challenges}
\input{sections/implications}
\input{sections/limitations}
\input{sections/conclusion}

\bibliographystyle{abbrv}
%\bibliographystyle{plain}
%\setlength{\bibsep}{3pt}
\small
\bibliography{paper}

### 2013-03-16 sections/outcomes.tex
Added figures and references to them
changed according to camera-ready formatting instructions

Our second research question seeks to understand what the actual outcomes of code reviews are, and whether they match the motivations and expectations outlined in the previous section. To that end, we conducted indirect field research~\cite{lethbridge2005studying} by analyzing the content of 200 threads (corresponding to 570 comments) recorded by CodeFlow. \figref{XXX4} shows the categories of comments found through the card sort.

@@

\subsection{Finding defects: When expectations do not meet reality}

>>>>

\begin{figure}[t] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=\columnwidth]{comments.pdf}
   \vspace{-1.5em}
   \caption{Proportion of comments by card sort category.}
   \label{fig:comments}
   \vspace{-1.5em}
\end{figure}

Our second research question seeks to understand what the actual outcomes of code reviews are, and whether they match the motivations and expectations outlined in the previous section. To that end, we conducted indirect field research~\cite{lethbridge2005studying} by analyzing the content of 200 threads (corresponding to 570 comments) recorded by CodeFlow. \figref{fig:comments} shows the categories of comments found through the card sort.

@@

\subsection{Finding Defects: When Expectations Do Not Meet Reality}
